\bf Faster Neural Machine Translation Inference

### 2018-02-02 fast-beam/fast-beam.tex
fast beam paper

Firstly, the number of classes in many deep-learning applications is small. However, the number of classes in NMT models is typically in the tens or hundreds of thousands, corresponding to the vocabulary size of the output language. For example, ~\cite{sennrich-haddow-birch:2016:P16-12} experimented with target vocabulary sizes of 60,000 and 90,000 subword units. This makes the output layer of NMT models very computationally expensive. Figure~\ref{fig:pie-time-europarl} shows the breakdown of amount of time during translation our NMT system; nearly 70\% of the time is involved in the output layer. We will look at optimizations which explicitly target the output layer.
\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{pie-time-europarl.png}} 
\end{tabular}
\caption{Proportion of time spent during translation (beam size 5, Europarl test set)}
\label{fig:pie-time-europarl}
\end{figure}

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{batch-size.png}} 
\end{tabular}
\caption{Actual batchsize during decoding (max batchsize 128, beam size 5, Europarl test set)}
\label{fig:batch-size}
\end{figure}

@@

For inference, we used and extend Amun~\citep{junczys2016neural}, the fastest open-source inference engine we are aware of for the model used in this paper. We uused a mini-batch of 128 sentences and maxi-batch 10 times the size of the mini-batch, unless otherwise stated.

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{pie-time-opensubtitles.png}} 
\end{tabular}
\caption{Proportion of time spent during translation (beam size 5, Opensubtitles test set)}
\label{fig:pie-time-opensubtitles}
\end{figure}

@@

After some experimentation, we decided fully fill the decoding batch only when it is at least half empty, rather than whenever a sentence has completed.

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{topup-europarl.png}} 
\end{tabular}
\caption{Translation speed for Europarl test set using top-up batching)}
\label{fig:topup-europarl}
\end{figure}

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{topup-opensubtitles.png}} 
\end{tabular}
\caption{Translation speed for OpenSubtitles test set using top-up batching)}
\label{fig:topup-opensubtitles}
\end{figure}

>>>>

Firstly, the number of classes in many deep-learning applications is small. However, the number of classes in NMT models is typically in the tens or hundreds of thousands, corresponding to the vocabulary size of the output language. For example, ~\cite{sennrich-haddow-birch:2016:P16-12} experimented with target vocabulary sizes of 60,000 and 90,000 subword units. This makes the output layer of NMT models very computationally expensive. Figure~\ref{fig:pie-time-europarl} shows the breakdown of amount of time during translation our NMT system; nearly 70\% of the time is involved in the output layer. We will look at optimizations which explicitly target the output layer.
\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{pie-time-europarl.png}} 
\end{tabular}
\caption{Proportion of time spent during translation (Europarl test set)}
\label{fig:pie-time-europarl}
\end{figure}

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{batch-size.png}} 
\end{tabular}
\caption{Actual batchsize during decoding (Europarl test set)}
\label{fig:batch-size}
\end{figure}

@@

For inference, we used and extend Amun~\citep{junczys2016neural}, the fastest open-source inference engine we are aware of for the model used in this paper. We used a beam size of 5, mini-batch of 128 sentences and maxi-batch 1280, unless otherwise stated.

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{pie-time-opensubtitles.png}} 
\end{tabular}
\caption{Proportion of time spent during translation (Opensubtitles test set)}
\label{fig:pie-time-opensubtitles}
\end{figure}

@@

After some experimentation, we decided to fully fill the decoding batch only when it is at least half empty, rather than whenever a sentence has completed.

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{topup-europarl.png}} 
\end{tabular}
\caption{Translation speed for Europarl test set using top-up batching}
\label{fig:topup-europarl}
\end{figure}

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{topup-opensubtitles.png}} 
\end{tabular}
\caption{Translation speed for OpenSubtitles test set using top-up batching}
\label{fig:topup-opensubtitles}
\end{figure}
